TITLE

### 2021-02-27 outputs/Paper.Rmd
update

* From figure1(Figure \@ref(fig:restaurant1)) and figure2(Figure \@ref(fig:restaurant2)), we noticed that more restaurants are located in Toronto (around 500) and Peel (around 400). The number of restaurants in Hilton is similar to the number in Durham. Meanwhile, Casual dining takes the lead in the restaurant type in GTA, with around 26%. Then it comes to Family style restaurant, accounting for 20%. Fast food restaurant, fine dining restaurant and Premium casual restaurant almost equally make up 10%.
There is no big difference between treated group and control group in terms of restaurant number and type distributions.

@@

The re-opening implementation enables the treated restaurants to operate indoor dining and patio services besides offering delivery and/or pickup as before during lockdown. The additional line of business attracts more customers to visit stores to order dishes and beverages. The increased food sales earn extra revenue for those restaurants. As demonstrated through the revenue histogram (Figure \@ref(fig:revenue1)), the treatment group has higher revenue levels overall than the control group. The restaurants follow binomial distributions based on restaurant sizes. Restaurant size and revenue level are positively correlated. According to the correlation heatmap (Figure \@ref(fig:correlation)), bigger restaurants generate more revenues than small ones. Restaurants having fewer than 20 employees are defined to be small, which are most of the cases in the total samples. Both small and big restaurants generate higher revenues in the treated group. The t-test [cross ref: t-table] further verifies our finding that the restaurants allowed for re-opening earn significantly more than the control group; the average revenue for the treated is \$63,144 while below \$5,000 for the control group.

>>>>

* From (Figure \@ref(fig:restaurant1)) and (Figure \@ref(fig:restaurant2)), we noticed that more restaurants are located in Toronto (around 500) and Peel (around 400). The number of restaurants in Hilton is similar to the number in Durham. Meanwhile, Casual dining takes the lead in the restaurant type in GTA, with around 26%. Then it comes to Family style restaurant, accounting for 20%. Fast food restaurant, fine dining restaurant and Premium casual restaurant almost equally make up 10%.
There is no big difference between treated group and control group in terms of restaurant number and type distributions.

@@

The re-opening implementation enables the treated restaurants to operate indoor dining and patio services besides offering delivery and/or pickup as before during lockdown. The additional line of business attracts more customers to visit stores to order dishes and beverages. The increased food sales earn extra revenue for those restaurants. As demonstrated through the revenue histogram (Figure \@ref(fig:revenue1)), the treatment group has higher revenue levels overall than the control group. The restaurants follow binomial distributions based on restaurant sizes. Restaurant size and revenue level are positively correlated. According to the correlation heatmap (Figure \@ref(fig:correlation)), bigger restaurants generate more revenues than small ones. Restaurants having fewer than 20 employees are defined to be small, which are most of the cases in the total samples. Both small and big restaurants generate higher revenues in the treated group. The t-test (Table \@ref(tab:ttest)) further verifies our finding that the restaurants allowed for re-opening earn significantly more than the control group; the average revenue for the treated is \$63,144 while below \$5,000 for the control group.
